Lab News

### 2024-04-12 index.qmd
change landing page image back to iwc
new paper accepted as news

![](images/uni-hall-front.jpg)

@@

@@

<font color="#d08770">[June 28 2023].</font> **New milestone**. Congratulations Dr. Laura St. Germain on a successfully defending your doctoral work.

>>>>

![](images/iwc-front.jpg)

@@

<font color="#d08770">[April 12 2024].</font> **Paper accepted**. McKay, B., Corson, A.E., Seedu, J., De Faveri, C.S., Hasan, H., Arnold, K., Adams, F.C., & Carter, M.J. Reporting bias, not external focus: A robust Bayesian meta-analysis and systematic review of the attentional focus literature. *Psychological Bulletin*.

@@
